A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Add BED reducedness notice

>>>>

Analogous to OBDDs and FDDs, OBEDs and FBEDs can be defined, whereas OBEDs are
OBDDs without operator nodes. The reduction rule of BEDs is similar to the one
of OBDDs but extended with an additional rule for operator nodes. For any operator
nodes $n$ it has to hold that $lo(n)$ and $hi(n)$ are nonterminals in order to
guarantee reducedness. However, even if a BED is reduced, canonicity is not
guaranteed (in contrast to OBDDs).
